Source Summaries

### 2020-03-30 paper/sourceSummaries/summary6.tex

\noindent
\subsection{Title}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
%\bibentry{filizzola2018security}

@@

\noindent
Main Idea

@@

\noindent
Theory

@@

\noindent
Method

@@

\noindent
Findings

@@

\noindent
Future Directions

>>>>

\noindent
\subsection{{I}nvestigations of {P}ower {A}nalysis {A}ttacks on {S}martcards}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{messerges_dabbish_sloan_1999}

@@

\noindent
The main idea of this paper is to analyze power anylysis techniques that had been used in the past to attack the DES encryption protocol. The authors then propose a method to model the signal vs noise ratio.

@@

\noindent
The main theory on display during this analysis is game theory, the authors treat the ability to measue power levels from the reader as a win in this scenario.

@@

\noindent
The authors were able to measure the power dissipation of the smartcard by reading from the ground pin with the assisstance of a small resistor in series between the VSS pin on the card and the true ground.

@@

\noindent
The authors confimed "that power analysis attacks can be quite powerful and need to be addressed." They also were able to successfully propose a way to model the noise characteristics of the power signal coming from the smartcard in hopes of inspiring future work to secure smartcard software against power analysis attacks.

@@

\noindent
The authors suggest that "Future research in this area will investigate power analysis attacks on hardware encryption devices and publickey cryptosystems." At the time this paper was written, AES had not yet been published so there definately room for more work on this topic.
